manuscript_outline

### 2025-07-01 docs/manuscript/paper.Rmd
added ref to table 2

**BCL NOTE: Thoughts on adding this marine copepod paper?** <https://doi.org/10.1086/662174>

| Class        | Order      | Genera         | Species            | Study                                     |
|:--------------|:--------------|:--------------|:--------------|:--------------|
| Amphibia     | Anura      | *Lithobates*   | *L. sylvaticus*    | @moore1939                                |
|              |            |                | *L. pipiens*       |                                           |
|              |            |                | *L. clamitans*     |                                           |
|              |            |                | *L. palustris*     |                                           |
|              |            | *Ascaphus*     | *A. truei*         | @brown1975                                |
|              | Urodela    | *Ambystoma*    | *A. gracile*       | @brown1976                                |
| Reptilia     | Squamata   | *Sceloporus*   | *S. undulatus*     | @angilletta2000                           |
|              |            | *Podarcis*     | *P. mural*is       | @vandamme1992                             |
|              | Testudines | *Mauremys*     | M. reevesii        | @du2007                                   |
|              |            |                | 181 species        | 141 studies in @while2018                 |
| Insecta      | Plecoptera | *Nemurella*    | *N. pictetii*      | @brittain1978, @elliott1984               |
|              |            | *Capnia*       | *C. atra*          | @brittain1984                             |
|              |            | *Capnia*       | *C. bifrons*       | @elliott1986                              |
|              |            | *Mesocapnia*   | *M. oenone*        | @brittain1984                             |
|              |            | *Taeniopteryx* | *T. nebulosa*      | @brittain1977                             |
|              | Coleoptera | *Colaphellus*  | *C. bowringi*      | @tang2017                                 |
|              |            |                | 18 species         | Developmental equations in @pritchard1987 |
| Malacostraca | Decapoda   | *Pontastacus*  | *P. leptodactylus* | @aydin2004                                |

>>>>

| Class        | Order         | Genera         | Species            | Study                                     |
|:--------------|:--------------|:--------------|:--------------|:--------------|
| Amphibia     | Anura         | *Lithobates*   | *L. sylvaticus*    | @moore1939                                |
|              |               |                | *L. pipiens*       |                                           |
|              |               |                | *L. clamitans*     |                                           |
|              |               |                | *L. palustris*     |                                           |
|              |               | *Ascaphus*     | *A. truei*         | @brown1975                                |
|              | Urodela       | *Ambystoma*    | *A. gracile*       | @brown1976                                |
| Reptilia     | Squamata      | *Sceloporus*   | *S. undulatus*     | @angilletta2000                           |
|              |               | *Podarcis*     | *P. mural*is       | @vandamme1992                             |
|              | Testudines    | *Mauremys*     | M. reevesii        | @du2007                                   |
|              |               |                | 181 species        | 141 studies in @while2018                 |
| Insecta      | Plecoptera    | *Nemurella*    | *N. pictetii*      | @brittain1978, @elliott1984               |
|              |               | *Capnia*       | *C. atra*          | @brittain1984                             |
|              |               | *Capnia*       | *C. bifrons*       | @elliott1986                              |
|              |               | *Mesocapnia*   | *M. oenone*        | @brittain1984                             |
|              |               | *Taeniopteryx* | *T. nebulosa*      | @brittain1977                             |
|              | Coleoptera    | *Colaphellus*  | *C. bowringi*      | @tang2017                                 |
|              |               |                | 18 species         | Developmental equations in @pritchard1987 |
| Malacostraca | Decapoda      | *Pontastacus*  | *P. leptodactylus* | @aydin2004                                |
| Copepoda     | Calanoida     | 13 genera      |                    | <https://doi.org/10.1086/662174>          |
|              | Cyclopoida    | 3 genera       |                    | <https://doi.org/10.1086/662174>          |
|              | Harpacticoida | 2 genera       |                    | <https://doi.org/10.1086/662174>          |
